%
% File semeval2020.tex
%
% Nathan Schneider
%% Based on the style files for COLING-2020 (feiliu@cs.ucf.edu & liang.huang.sh@gmail.com), which were, in turn,
%% Based on the style files for COLING-2018, which were, in turn,
%% Based on the style files for COLING-2016, which were, in turn,
%% Based on the style files for COLING-2014, which were, in turn,
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{coling2020}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{microtype}

\hyphenation{an-aly-sis}
\hyphenation{an-aly-ses}
\hyphenation{Sem-Eval}

%\setlength\titlebox{5cm}
\colingfinalcopy % Uncomment this line for all SemEval submissions

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.


\title{SemEval-2020 Task [12]: [Transfer Learning for Offensive Language Detection using XLM-Roberta]}

\author{Michael Zeng\\
  School of Information\\
  University of California, Berkeley \\
  {\tt zengm71@berkeley.edu} \\\And
  Yekun  Wang\\
  School of Information\\
  University of California, Berkeley \\
  {\tt myekun.wang@berkeley.edu} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a paper submitted
  to SemEval-2020 or accepted for publication in its proceedings. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers. Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Introduction}
\label{intro}



\section*{Acknowledgements}

The acknowledgements should go immediately before the references.  Do
not number the acknowledgements section. Do not include this section
when submitting your paper for review.

% include your own bib file like this:
\bibliographystyle{coling}
\bibliography{semeval2020}

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Zampieri, Marcos  and
      Malmasi, Shervin  and
      Nakov, Preslav  and
      Rosenthal, Sara  and
      Farra, Noura  and
      Kumar, Ritesh
\newblock 2019.
\newblock {\em Predicting the Type and Target of Offensive Posts in Social Media}
\newblock Association for Computational Linguistics
\end{thebibliography}

\end{document}
